The complex network of trophic interactions in a subAntarctic Marine Protected Area

### 2023-03-29 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Version sent to co-authors (?)

---
title: The complex network of trophic interactions in a subAntarctic Marine Protected
  Area
author:
  - name: Tomás I. Marina^a^
    email: tomasimarina@gmail.com
  - name: Irene R. Schloss^a^^,^^b^
  - name: Luciana Riccialdelli^a^
  - name: To be continued(?)^c^
address:
  - code: 1
    address: Centro Austral de Investigaciones Cientificas (CADIC-CONICET), Argentina
  - code: 2
    address: Instituto Antartico Argentino (IAA), Argentina
  - code: 3
    address: INIDEP, UBA-CONICET, IIMyC-CONICET, MACN-CONICET, UNC-CONICET
abstract: |
  Globally, the total area of the world ocean designated under marine protection has increased in the recent decades. The majority of these Marine Protected Areas (MPAs) focus on the presence of particularly vulnerable, keystone, or charismatic species, the presence of large numbers (or proportions) of endemic species, and/or the presence of high biodiversity across taxonomic levels. In the sub-Antarctic region, the level of ocean protection is mainly associated to oceanic islands, except for the MPAs Namuncurá - Banco Burdwood I and II (MPA N-BB), which are associated to a submarine plateau and its southern adjacent deep slope region, respectively. Here we present the first detailed analysis of the network of predator-prey interactions (food web) for the MPA N-BB ecosystem. We applied a network approach with the objective of characterize the food web in terms of complexity and structure, and identify the species' role in such framework.

>>>>

---
title: The complex network of trophic interactions in a subAntarctic Marine Protected
  Area
author:
  - name: Tomás I. Marina^a^
    email: tomasimarina@gmail.com
  - name: Irene R. Schloss^a^^,^^b^
  - name: Luciana Riccialdelli^a^
  - name: To be continued(?)^c^
address:
  - code: 1
    address: Centro Austral de Investigaciones Cientificas (CADIC-CONICET), Argentina
  - code: 2
    address: Instituto Antartico Argentino (IAA), Argentina
  - code: 3
    address: INIDEP, UBA-CONICET, IIMyC-CONICET, MACN-CONICET, UNC-CONICET
abstract: |
  Globally, the total area of the world ocean designated under marine protection has increased in the recent decades. The majority of these Marine Protected Areas (MPAs) focus on the presence of particularly vulnerable, keystone, or charismatic species, the presence of large numbers of endemic species, and/or the presence of high biodiversity across taxonomic levels. In the sub-Antarctic region, the level of ocean protection is mainly associated to oceanic islands, except for the MPAs Namuncurá - Banco Burdwood I and II (MPA N-BB, 53º–55ºS and 56º–62ºW), which are associated to a submarine plateau and its southern adjacent deep slope region, respectively. Here we present the first detailed analysis of the network of predator-prey interactions (food web) for the MPA N-BB ecosystem. We applied a network approach with the objective of characterizing the food web in terms of complexity and structure, and identifying the species' role in such framework. In terms of complexity, the MPA N-BB food web consisted of 1778 predator-prey interactions and 379 species, with a link density of 4.69 and a connectance of 0.01. In terms of structure, almost half of the consumers were omnivores (0.48), and the network displayed a small-world pattern. All this suggest that the ecosystem might be fragile to external perturbations targeting highly connected species, although structural properties might provide resilience and resistance with the final outcome of a rearrange structure maintaining their functions. On the other hand, we identified several species as important in terms of different aspects of trophic structure and functioning, and response to perturbations. We suggest that generalist species, mostly fishes, play a crucial role in the ecosystem's bentho-pelagic coupling process. In addition, we propose that other species rather than the longtail southern cod *Patagonotothen ramsayi* and the Fueguian sprat *Sprattus fuegensis* should be considered as relevant energy transfers for the ecosystem. Finally, we argue that it is the diversity of species, representing the benthic and pelagic habitats, what maintains the connectivity of the food web against perturbations, therefore contributing to the structure and stability of the ecosystem.

### 2023-03-29 MS_ToSubmit/MS_Burdwood_foodweb.tex
Version sent to co-authors (?)

  \begin{abstract}
  The abstract goes here.
  \end{abstract}
    \begin{keyword}
    Food web \sep Complexity \sep Structure \sep Marine Protected
Area \sep 
    Southwest Atlantic
  \end{keyword}

>>>>

  \begin{abstract}
  Globally, the total area of the world ocean designated under marine
  protection has increased in the recent decades. The majority of these
  Marine Protected Areas (MPAs) focus on the presence of particularly
  vulnerable, keystone, or charismatic species, the presence of large
  numbers of endemic species, and/or the presence of high biodiversity
  across taxonomic levels. In the sub-Antarctic region, the level of
  ocean protection is mainly associated to oceanic islands, except for
  the MPAs Namuncurá - Banco Burdwood I and II (MPA N-BB, 53º--55ºS and
  56º--62ºW), which are associated to a submarine plateau and its
  southern adjacent deep slope region, respectively. Here we present the
  first detailed analysis of the network of predator-prey interactions
  (food web) for the MPA N-BB ecosystem. We applied a network approach
  with the objective of characterizing the food web in terms of
  complexity and structure, and identifying the species' role in such
  framework. In terms of complexity, the MPA N-BB food web consisted of
  1778 predator-prey interactions and 379 species, with a link density
  of 4.69 and a connectance of 0.01. In terms of structure, almost half
  of the consumers were omnivores (0.48), and the network displayed a
  small-world pattern. All this suggest that the ecosystem might be
  fragile to external perturbations targeting highly connected species,
  although structural properties might provide resilience and resistance
  with the final outcome of a rearrange structure maintaining their
  functions. On the other hand, we identified several species as
  important in terms of different aspects of trophic structure and
  functioning, and response to perturbations. We suggest that generalist
  species, mostly fishes, play a crucial role in the ecosystem's
  bentho-pelagic coupling process. In addition, we propose that other
  species rather than the longtail southern cod \emph{Patagonotothen
  ramsayi} and the Fueguian sprat \emph{Sprattus fuegensis} should be
  considered as relevant energy transfers for the ecosystem. Finally, we
  argue that it is the diversity of species, representing the benthic
  and pelagic habitats, what maintains the connectivity of the food web
  against perturbations, therefore contributing to the structure and
  stability of the ecosystem.
  \end{abstract}
    \begin{keyword}
    Food web \sep Complexity \sep Structure \sep Marine Protected
Area \sep 
    Southwest Atlantic
  \end{keyword}
